|

### 2021-09-09 article/article.Rmd
main paper function

  if (!is.null(caption)){
    if (!is.character(caption))
      stop(" argument 'caption' must be a character'")
  } else {
    if (ww==1){
      if (attr(x,"groups"))
        if (inherits(x,"missingTable"))
          caption<-paste("Missingness table by groups of `",y.name.label,"'",sep="")
      else
        caption<-paste("Summary descriptives table by groups of `",y.name.label,"'",sep="")
      else
        if (inherits(x,"missingTable"))
          caption<-"Missingess table"
        else
          caption<-"Summary descriptives table"
    }
    if (ww==2){
      if (attr(x,"groups"))
        caption<-paste("Available data by groups of `",y.name.label,"'",sep="")
      else
        caption<-"Available data"
    }
  }
  pp <- compareGroups:::prepare(x, nmax = nmax, header.labels)
  #pp <- prepare(x, nmax = nmax, header.labels)
  cc <- unlist(attr(pp, "cc"))
  if (ww %in% c(1)) {
    table1 <- pp[[1]]
    ii <- ifelse(rownames(table1)[2] == "", 2, 1)
    table1 <- cbind(rownames(table1), table1)
    align <- c("l", rep("c", ncol(table1)))
    table1[1, 1] <- " "
    colnames(table1) <- table1[1, ]
    colnames(table1)[-1] <- trim(colnames(table1)[-1])
    table1 <- table1[-1, , drop = FALSE]
    table1[,2:ncol(table1)] <- apply(table1[,-1,drop=FALSE],2,trim)
    #table1 <- table1[-2]
    #names(table1)[1] <- 'Extended Sample'
    # N in the second row
    table1 <- table1[,-3]
    colnames(table1)[2] <- 'Extended Sample'
    n.exists <- nrow(table1) > 1 && length(grep("^N=", trim(table1[1, 2])))
    if (format=="latex" & strip)
      table1[((1+n.exists):nrow(table1)),ncol(table1)] <- ifelse(table1[((1+n.exists):nrow(table1)),ncol(table1)]=="", "\\vphantom{}", table1[((1+n.exists):nrow(table1)),ncol(table1)])
    if (format=="latex") caption <- gsub("%","\\\\%",caption)
    ans <- knitr::kable(table1, align = align, row.names = FALSE, caption=caption[1], format=format,
                        booktabs=format=="latex", longtable=TRUE, linesep="", ...)
    ans <- add_indent(ans, grep("^ ",table1[,1]))
    if (width!=Inf) ans <- column_spec(ans, 1, width = width)
    # groups
    if (!is.null(cc)){
      for (cci in 1:length(cc)){
        if (cc[cci]!=""){
          group.label <- cc[cci]
          inici <- 0
          final <- 0
        } else {
          if (cc[cci-1]!="")
            group.begin <- cci-1
          if (cci==length(cc) || cc[cci+1]!=""){
            group.end <- cci
            ans <- group_rows(ans, group.label, group.begin+n.exists, group.end+n.exists)
          }
        }
      }
    }
    if (strip){
      nr <- attr(pp, "nr")
      ans <- row_spec(ans, which(nr==!first.strip)+n.exists, background = background)
    }
    if (n.exists){
      ans <- row_spec(ans, 1, hline_after=TRUE)
    }

@@

aux3 <- descrTable(~.-usemeta2, 
                   aux, y = aux$usemeta2,
                   show.p.overall = F, 
                   show.all = T)
export2md2(aux3, 
           caption = "Descriptive Statistics of Moderators", 
           format  = "latex")
```
\normalsize

>>>>

  if (!is.null(caption)){
    if (!is.character(caption))
      stop(" argument 'caption' must be a character'")
  } else {
    if (ww==1){
      if (attr(x,"groups"))
        if (inherits(x,"missingTable"))
          caption<-paste("Missingness table by groups of `",y.name.label,"'",sep="")
      else
        caption<-paste("Summary descriptives table by groups of `",y.name.label,"'",sep="")
      else
        if (inherits(x,"missingTable"))
          caption<-"Missingess table"
        else
          caption<-"Summary descriptives table"
    }
    if (ww==2){
      if (attr(x,"groups"))
        caption<-paste("Available data by groups of `",y.name.label,"'",sep="")
      else
        caption<-"Available data"
    }
  }
  pp <- compareGroups:::prepare(x, nmax = nmax, header.labels)
  #pp <- prepare(x, nmax = nmax, header.labels)
  cc <- unlist(attr(pp, "cc"))
  if (ww %in% c(1)) {
    table1 <- pp[[1]]
    ii <- ifelse(rownames(table1)[2] == "", 2, 1)
    table1 <- cbind(rownames(table1), table1)
    align <- c("l", rep("c", ncol(table1)))
    table1[1, 1] <- " "
    colnames(table1) <- table1[1, ]
    colnames(table1)[-1] <- trim(colnames(table1)[-1])
    table1 <- table1[-1, , drop = FALSE]
    table1[,2:ncol(table1)] <- apply(table1[,-1,drop=FALSE],2,trim)
    #table1 <- table1[-2]
    #names(table1)[1] <- 'Extended Sample'
    # N in the second row
    table1 <- table1[,-3]
    colnames(table1)[2] <- 'Extended Sample'
    table1 <- table1[,c(1,3,2)]
    n.exists <- nrow(table1) > 1 && length(grep("^N=", trim(table1[1, 2])))
    if (format=="latex" & strip)
      table1[((1+n.exists):nrow(table1)),ncol(table1)] <- ifelse(table1[((1+n.exists):nrow(table1)),ncol(table1)]=="", "\\vphantom{}", table1[((1+n.exists):nrow(table1)),ncol(table1)])
    if (format=="latex") caption <- gsub("%","\\\\%",caption)
    ans <- knitr::kable(table1, align = align, row.names = FALSE, caption=caption[1], format=format,
                        booktabs=format=="latex", longtable=TRUE, linesep="", ...)
    ans <- add_indent(ans, grep("^ ",table1[,1]))
    if (width!=Inf) ans <- column_spec(ans, 1, width = width)
    # groups
    if (!is.null(cc)){
      for (cci in 1:length(cc)){
        if (cc[cci]!=""){
          group.label <- cc[cci]
          inici <- 0
          final <- 0
        } else {
          if (cc[cci-1]!="")
            group.begin <- cci-1
          if (cci==length(cc) || cc[cci+1]!=""){
            group.end <- cci
            ans <- group_rows(ans, group.label, group.begin+n.exists, group.end+n.exists)
          }
        }
      }
    }
    if (strip){
      nr <- attr(pp, "nr")
      ans <- row_spec(ans, which(nr==!first.strip)+n.exists, background = background)
    }
    if (n.exists){
      ans <- row_spec(ans, 1, hline_after=TRUE)
    }

@@

aux3 <- descrTable(~.-usemeta2, 
                   aux, y = aux$usemeta2,
                   show.p.overall = F, 
                   show.all = T)
export2md2(aux3, 
           caption = "Descriptive Statistics of Moderators", 
           format  = "latex")

```
\normalsize
